---
title: "R Programming Quiz 1"
author: "Francisco Martín"
date: "September, 2018"
output: html_document
---

## 1.-

The R language is a dialect of which of the following programming languages?

- Lisp

- Fortran

- S  (Correct)

- Scheme

Solution -> Theory



## 2.-

The definition of free software consists of four freedoms (freedoms 0 through 3). Which of the following is NOT one of the freedoms that are part of the definition? Select all that apply.

- The freedom to run the program, for any purpose.

- The freedom to restrict access to the source code for the software.  (Correct)

- The freedom to redistribute copies so you can help your neighbor.

- The freedom to prevent users from using the software for undesirable purposes.  (Correct)

- The freedom to study how the program works, and adapt it to your needs.

- The freedom to sell the software for any price.   (Correct)

- The freedom to improve the program, and release your improvements to the public, so that the whole community benefits.


Solution -> Theory


## 3.-

In R the following are all atomic data types EXCEPT: (Select all that apply)

- integer

- character

- table  (Correct)

- logical

- data frame  (Correct)

- numeric

- matrix  (Correct)

- complex

- array   (Correct)

- list    (Correct)


Solution -> Theory


## 4.-

If I execute the expression x <- 4L in R, what is the class of the object `x' as determined by the `class()' function?

- numeric  (Correct)

- matrix

- logical

- integer  (Correct)

- character

- complex


Solution -> Just prove it:

```{r prove_4}
x <- 4L
class(x)
```


## 5.-

What is the class of the object defined by x <- c(4, TRUE)?

- numeric (Correct)

- logical

- matrix

- character

- integer

- list

Solution -> Logical will be converted to numeric 1, and x will be numeric, but prove it

```{r prove_5}
x <- c(4,TRUE)
class(x)
```


## 6.-

If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)?

- a matrix with two rows and three columns  (Correct)

- a vector of length 2

- a vector of length 3

- a 3 by 3 matrix

- a 3 by 2 matrix  

- a 2 by 2 matrix
 

Solution -> It combines the two vectors as columns. Prove:

```{r prove_6}
x <- c(1,3, 5);  y <- c(3, 2, 10);
rbind(x, y)
```



## 7.-

A key property of vectors in R is that

- elements of a vector all must be of the same class  (Correct)

- elements of a vector can only be character or numeric

- the length of a vector must be less than 32,768

- elements of a vector can be of different classes

- a vector cannot have have attributes like dimensions



Solution -> Theory


## 8.-

Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[2]] give me? Select all that apply.

- a list containing a character vector with the elements "a" and "b".

- a character vector of length 1.  (Correct)

- a list containing character vector with the letter "a".

- a character vector containing the letter "a".  (Correct)

- a character vector with the elements "a" and "b".



Solution -> Let`s prove it

``` {r prove_8}
x <- list(2, "a", "b", TRUE)
x[[2]]
```


## 9.-

Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?


- a numeric vector with elements 3, 2, 3, 4.

- a numeric vector with elements 1, 2, 3, 6.

- an integer vector with elements 3, 2, 3, 4.

- a numeric vector with elements 3, 2, 3, 6.

- an integer vector with elements 3, 2, 3, 6.

- a numeric vector with elements 3, 4, 5, 6.  (Correct)



Solution -> Just prove:

``` {r prove_9}
x <- 1:4; y <- 2;
x + y
```


## 10.-

Suppose I have a vector x <- c(17, 14, 4, 5, 13, 12, 10) and I want to set all elements of this vector that are greater than 10 to be equal to 4. What R code achieves this? Select all that apply.

- x[x >= 11] <- 4  (Correct)

- x[x == 4] > 10

- x[x < 10] <- 4

- x[x == 10] <- 4

- x[x > 4] <- 10

- x[x >= 10] <- 4

- x[x > 10] <- 4  (Correct)

- x[x > 10] == 4


Solution -> Logic


## 11.-

Use the Week 1 Quiz Data Set to answer questions 11-20.

In the dataset provided for this Quiz, what are the column names of the dataset?

- Ozone, Solar.R, Wind, Temp, Month, Day  (Correct)

- Ozone, Solar.R, Wind

- 1, 2, 3, 4, 5, 6

- Month, Day, Temp, Wind

Solution ->

``` {r prove_11}

url <- "https://d396qusza40orc.cloudfront.net/rprog/data/quiz1_data.zip"
path <- file.path(getwd(),"hw1_data.csv")

if (!file.exists(path)){
        download.file(url,path)
}

data <- read.csv(path)
names(data)

```


## 12.-
Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

- ` Ozone Solar.R Wind Temp Month Day
1     9      24 10.9   71     9  14
2    18     131  8.0   76     9  29 `

- ` Ozone Solar.R Wind Temp Month Day
1    18     224 13.8   67     9  17
2    NA     258  9.7   81     7  22`

- ` Ozone Solar.R Wind Temp Month Day
1    41     190  7.4   67     5   1
2    36     118  8.0   72     5   2`   (Correct)

- `   Ozone Solar.R Wind Temp Month Day
1     7      NA  6.9   74     5  11
2    35     274 10.3   82     7  17`


Solution ->

``` {r prove_12}
data[c(1,2),]
```


## 13.-

How many observations (i.e. rows) are in this data frame?

- 129

- 45

- 153 (Correct)

- 160

Solution -> 
```{r prove_13}
dim(data)[1]
```



## 14.-

Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

- ` Ozone Solar.R Wind Temp Month Day
152    34     307 12.0   66     5  17
153    13      27 10.3   76     9  18`

- ` Ozone Solar.R Wind Temp Month Day
152    11      44  9.7   62     5  20
153   108     223  8.0   85     7  25`

- ` Ozone Solar.R Wind Temp Month Day
152    31     244 10.9   78     8  19
153    29     127  9.7   82     6   7`   

- ` Ozone Solar.R Wind Temp Month Day
152    18     131  8.0   76     9  29
153    20     223 11.5   68     9  30`  (Correct)

Solution ->

``` {r prove_14}
data[c(dim(data)[1]-1,dim(data)[1]),]
```


## 15.-

What is the value of Ozone in the 47th row?

- 34

- 63

- 21  (Correct)

- 18

Solution ->
``` {r prove_15}
data[47,]$Ozone
```

## 16.-

How many missing values are in the Ozone column of this data frame?

- 37  (Correct)

- 43

- 78

- 9

Solution ->

``` {r prove_16}
sum(is.na(data$Ozone))
```

## 17.-

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

- 42.1

- 18.0

- 31.5

- 53.2

Solution ->

``` {r prove_17}
# Select data except (-) columns which Ozone is NA, do the mean and round to 1 decimal
round(mean(data[-which(is.na(data$Ozone)),]$Ozone),1)
```

## 18.-

Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

- 185.9

- 205.0

- 334.0

- 212.8  (Correct)

Solution ->

``` {r prove_18}
mean(data[which(data$Ozone>31 & data$Temp>90),]$Solar.R)
```

## 19.-

What is the mean of "Temp" when "Month" is equal to 6?

- 79.1  (Correct)

- 75.3

- 90.2

- 85.6

Solution ->

``` {r prove_19}
mean(data[which(data$Month==6),]$Temp)
```

## 20.-

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?

- 18

- 97

- 100

- 115 (Correct)

Solution ->

``` {r prove_20}
max(data[which(data$Month==5 & !is.na(data$Ozone)),]$Ozone)
```
